Healthcare Insights and Sociodemographic Analysis of New York: A Comprehensive Analysis of Patient Records in 2013

### 2023-09-30 STAT405Project.qmd
Added plots

## Plot 9: Boxplots on the Total Costs on the Risk of Mortality

@@

@@

>>>>

## Plot 9:

@@

```{r warning = FALSE}
#| echo: false
ggplot(cleaned_data, aes(x = cleaned_data$`Length of Stay`, y = cleaned_data$`Total Charges`))+
  geom_point(size = 0.2) +
  facet_grid(Race ~ `Type of Admission`) +
  labs(title = "Length of Stay v. Total Charges", x = "Length of Stay", y = "Total Charges")

@@

```{r warning = FALSE}
#| echo: false
ggplot(cleaned_data, aes(x = `Total Costs`)) +
  geom_density(fill = "blue", alpha = 0.5) +
  facet_grid(`Age Group` ~ .)
  labs(title = "Density Plot Example", x = "X-axis Label", y = "Density")
